A practical guide for selecting the spectral photon flux density distribution of light during the measurements of the leaf photosynthetic rate

### 2016-07-27 Sup1.Rmd
第０稿完成。3327 words

Information of the light sources and measuring instruments.

@@

SPD_labels <-
  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 750),
             value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf transmitted sunlight"),
             panel = rep(panel_names,  c(3, 4, 2)))

SPDs <-
  Sun %>%
  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
  select(-Absorptance) %>%
  gather(variable, value, -wavelength) %>%
  mutate(panel = panel_names[3]) %>%
  bind_rows(., OceanSPDs, LEDs) %>%
  filter(between(wavelength, 380, 820)) %>%
  ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
  theme_bw2() +
  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
  geom_line() +
  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
  scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey50", "black", "black")) +
  # facet_grid(panel ~ .) +
  facet_wrap(~ panel, ncol = 1) +
  gg_xy(c(380, 820, 0, 4.5)) +
  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))

CapSPD <-
  "Fig. S1  The spectral photon flux density distributions of light provided by (A) high-intensity dischage lamps (HIDs) and fluorescent lamps, (B) light-emitting diodes (LEDs), and (C) incident and leaf transmitted sunlight (see also Table S1). The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown. The distribution of sunlight was adopted from JIS C 8904-3. The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016). The far-red waveband (700--750 nm) is filled in grey."
```

@@

| Light source (abbreviation)     | Model code                    | Measuring instrument              |
|:--------------------------------|:------------------------------|:----------------------------------|
| Fluorescent lamp (FL)           | FPL55EX-N<sup>\*1</sup>       | HR2000 (Ocean Optics Inc.)        |
| Metal halide lmap (MH)          | M220FCELS-W/BUD<sup>\*1</sup> | HR2000 (Ocean Optics Inc.)        |
| High-pressure sodium lamp (HPS) | NH220FLS<sup>\*1</sup>        | HR2000 (Ocean Optics Inc.)        |
| Blue LED (B)                    | HBL3-3S55-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) |
| Red LED (R)                     | SRK3-3A80-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) |
| Far-red LED (FR)                | L735-36AU<sup>\*3</sup>       | MS-720 (EKO Instruments Co. Ltd.) |
| White LED (W)                   | NSPW310DS<sup>\*4</sup>       | MS-720 (EKO Instruments Co. Ltd.) |

>>>>

@@

SPD_labels <-
  data_frame(variable = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sun", "Shade"),
             wavelength = c(435, 520, 570, 448, 660, 735, 460, 450, 700),
             value = c(2.2, .6, 3, 4, 4.2, 3.8, 1.3, 0.6, 2),
             label = c("FL", "MH", "HPS", "B", "R", "FR", "W", "Sunlight", "Leaf transmitted sunlight"),
             panel = rep(panel_names,  c(3, 4, 2)))

SPDs <-
  Sun %>%
  SPDnorm(from = 350, to = 750, integratedPFD = IntegratePFD) %>%
  select(-Absorptance) %>%
  gather(variable, value, -wavelength) %>%
  mutate(panel = panel_names[3]) %>%
  bind_rows(., OceanSPDs, LEDs) %>%
  filter(between(wavelength, 380, 820)) %>%
  # ggplot(aes(x = wavelength, y = value, group = variable, col = variable, linetype = variable)) +
  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
  theme_bw2() +
  geom_rect(aes(xmin = 700, xmax = 750, ymin = 0, ymax = +Inf), fill = "grey90", col = NA) +
  geom_line() +
  geom_text(data = SPD_labels, aes(x = wavelength, y = value, label = label)) +
  # scale_linetype_manual(values = c(1, 1, 3, 2, 4, 2, 2, 1, 4)) +
  scale_color_manual(values = c("blue", "black", "darkred", "orange", "purple", "red", "grey50", "black", "black")) +
  # facet_grid(panel ~ .) +
  facet_wrap(~ panel, ncol = 1) +
  gg_xy(c(380, 820, 0, 4.5)) +
  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))

CapSPD <-
  "Fig. S1  The spectral photon flux density distributions of light provided by (A) high-intensity discharge lamps (HIDs) and fluorescent lamps, (B) light-emitting diodes (LEDs), and (C) incident and leaf transmitted sunlight (see also Table S1). The distributions at a photon flux density of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown. The distribution of sunlight was adopted from JIS C 8904-3. The distribution of the leaf transmitted sunlight was calculated from that of sunlight and the transmittance spectrum of a cucumber leaf (Murakami et al. 2016). The far-red waveband (700--750 nm) is filled in grey."
```

Information of the spectral distributions of artificial assimilation light and sunlight.

@@

| Light source (abbreviation)     | Model code                    | Measuring instrument              |
|:--------------------------------|:------------------------------|:----------------------------------|
| Fluorescent lamp (FL)           | FPL55EX-N<sup>\*1</sup>       | HR2000 (Ocean Optics Inc.)        |
| Metal halide lamp (MH)          | M220FCELS-W/BUD<sup>\*1</sup> | HR2000 (Ocean Optics Inc.)        |
| High-pressure sodium lamp (HPS) | NH220FLS<sup>\*1</sup>        | HR2000 (Ocean Optics Inc.)        |
| Blue LED (B)                    | HBL3-3S55-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) |
| Red LED (R)                     | SRK3-3A80-LE<sup>\*2</sup>    | MS-720 (EKO Instruments Co. Ltd.) |
| Far-red LED (FR)                | L735-36AU<sup>\*3</sup>       | MS-720 (EKO Instruments Co. Ltd.) |
| White LED (W)                   | NSPW310DS<sup>\*4</sup>       | MS-720 (EKO Instruments Co. Ltd.) |
